\documentclass[11pt]{exam}
\usepackage{epsfig}

\usepackage{hyperref}

\usepackage[centertags]{amsmath}
%\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[all]{xy}
\usepackage{newlfont}
\usepackage{amsmath,amssymb,bm,mathtools}

\usepackage{xcolor} %for color
\usepackage{xmpmulti}
%\usetheme{Air}
%\usefonttheme{professionalfonts}
\usepackage{thumbpdf}
\usepackage{wasysym}
\usepackage{upgreek}
\usepackage{ucs}
%\usepackage[utf8]{inputenc}
\usepackage{pgf,pgfarrows,pgfnodes,pgfautomata,pgfheaps,pgfshade}
\usepackage{verbatim}
\usepackage{empheq}
\newcommand*\widefbox[1]{\fbox{\hspace{2em}#1\hspace{2em}}}

\newcommand{\Integer}{\mathbb{Z}}
\newcommand{\Natural}{\mathbb{Z}_{\geq 0}}
\newcommand{\Naturalstar}{\mathbb{Z}_{> 0}}
\newcommand{\Real}{\mathbb{R}}
\newcommand{\Complex}{\mathbb{C}}
\newcommand{\hilbert}{\mathcal{H}}
\newcommand{\BigHilbert}{\bm{\mathcal{H}}}
\newcommand{\innprod}[2]{\langle{#1},{#2}\rangle}
\newcommand{\ginnprod}[2]{\langle\!\langle{#1},{#2}\rangle\!\rangle}
\newcommand{\norm}[1]{\|{#1}\|}
\newcommand{\mrm}[1]{{\mathrm #1}}
\newcommand{\gnorm}[1]{|\!|\!|{#1}|\!|\!|}
\newcommand{\expect}{\mathbb{E}}

\newcommand{\gr}{\selectlanguage{greek}}

%\newcommand{\red}{\color{myred}}
%\newcommand{\blue}{\color{myblue}}
%\newcommand{\black}{\color{myblack}}


%\definecolor{BrickRed}{cmyk}{0,0.89,0.94,0.28}
%\definecolor{pink}{RGB}{255,192,203}

\begin{document}
\centerline{\Large \sc Homework 1}
\pagestyle{empty}

\hrulefill

\vspace{2cm}


{\Large \sc Name:}



\vspace{2cm}



{\Large \sc Student ID:}

\vspace{6cm}

\begin{itemize}
  \item Reasoning and work must be shown to gain partial/full
  credit
  \item Please include the cover-page on your homework PDF with your name and student ID. Failure of doing so is considered bad citizenship. 

 \end{itemize}

\clearpage
\begin{questions}
\question[1--4]{\bf Modeling question}:
Indicate what kind of network model among the following
\begin{enumerate}
\item Undirected, unweighted
\item Undirected, weighted
\item Directed, unweighted
\item Directed, weighted
\item Directed, labeled
\end{enumerate}
you think is would be useful to study the following systems:
\begin{enumerate}
\item An ontology 
\item Twitter retweet network
\item The Internet
\item The electric grid
\end{enumerate}
and provide a short justification. 

\question[1--4]{\bf Bipartite graph question}:
 Assume Netflix's movie library contains
approximately 100,000 titles. 
 Netflix keeps data on customer preferences using a big bipartite network connecting users to titles they have watched and/or rated. These data are represented as a bipartite weighted graph connecting customers with movie with edge weight equal to the rating. 
\begin{parts}
\part In the fourth quarter of 2013, Netflix reported having a set of 33 million users. Assume the average user's degree in this network is 1000. Approximately how many links are in this
network? Would you consider this network sparse or dense? Explain.
\part Suppose that from 2013 to 2014 Netflix's library has remained the same size (100,000 titles), while the number of users has increased. Further suppose that the average user's degree in this network has remained constant. Has the density of this network increased, decreased, or stayed the same? 
\end{parts} 
{\color{blue}\it Hint: In lecture 2 we introduced the notionw of average degree, graph density and also the ``Handshaking theorem", which is what you need to use to answer these questions. } 


\question[1--4]{\bf Python/NetworkX questions}:  Please find two datasets in the attached files, i.e., ieee30.edgelist and ieee123.edgelist\footnote{Both these files represent the topologies of test cases of electric grids.}, and finish the follow questions using Python/NetworkX.
\begin{parts}
\part Plot the 30-node graph, and find the density, the maximal degree of the graph. 

\part Plot the 123-node graph, and find the density, the maximal degree of such a graph?  Is this graph connected? 

\part Does this graph have  cycles? If yes, please give an example. 

%\part Identify the minimum cut of the 30 as well as the 123 node bus using Networkx
%function \href{https://networkx.org/documentation/stable/reference/algorithms/generated/networkx.algorithms.flow.minimum_cut.html}{minimum\_cut}. Do they have a bridge?
\part Identify a cut of the 30 node bus system. Do they have a bridge?

\part Verify the {\it Handshaking theorem} for both graphs. 

\part Use the function in NetworkX called \href{https://networkx.org/documentation/stable/reference/algorithms/shortest_paths.html}{\tt shortest\_path}. Find the shortest path from node ``1" to node ``30" of  the 30-node system and  plot this path with another color in the graph.


{\color{blue}\it Hint: 
The packages that you need to include are networkx, matplotlib and numpy. 
}  
\end{parts}
\end{questions}

\end{document}




